%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Director of Operations} % Job title
    {DeSci Labs} % Organization
    {2022 - Present} % Location
    {Online} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {First employee hired to a newly formed big-data, blockchain, open-science startup. Established hiring processes and played a pivotal role in selecting, onboarding, and training a 20-person team. Served as the initial point of contact for a seed-round raise of \$4M at a \$20M valuation}
        \item {Built and managed relations with a network of 50+ archival-focused datacenters. Negotiated contracts with datacenters and served as technological advisor/white-glove concierge for end users during data transfer of over 1PB}  
        \item {Aligned domain-specific metadata of end-user datasets with higher-ed industry wide best practices by ensuring proper usage of controlled vocabularies as descriptors for datasets. Necessecary prerequesite for eventual LLM training and Knowledge Graph creation on data. Taught courses on the creation and communal management of RDF-based ontologies within academic research}  
        \item {Created a 2,000+ person product support community, founded three separate 1,000+ person conferences, and built a 50+ person community of high-profile academics championing company technologies. Established management processes, hired and trained community managers, then managed day-to-day in addition to overseeing finances and strategic direction. Over a three year span, these communities and conferences resulted in six grant opportunities totaling upwards of €20M+, 10+ academic conference proposals, and 25+ non-academic conference speaking spots}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Transformation and Product Management} % Job title
    {Ernst and Young} % Organization
    {2019 - 2022} % Location
    {Boise, Idaho U.S.A.} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Assisted a new CIO at a Fortune 100 construction company in strategizing, planning, and executing an IT-wide product transformation. Conducted feasibility assessments through end-to-end evaluations of IT capabilities and an IT financial analysis}
        \item {Identified high-potential areas for catalyst product teams by mapping HR, Finance, and Construction verticals. Capability mapping in the construction vertical included creating a value stream from scratch based on user interviews}
        \item {Acted as the "showcase" product owner during the transformation, building an internal tool while collaborating with executives and division leaders to demonstrate product thinking. Led and taught a product team of client side designers, developers, and product analysts, culminating in a 100+ page "Product Owner Manual" deliverable}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cybersecurity Audit Consultant} % Job title
    {} % Organization
    {} % Location
    {Silver Springs, Maryland U.S.A.} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Performed cybersecurity application landscape rationalization for a national healthcare organization. Identified 25+ underutilized or overlapping applications whose retirement saved over \$12M and facilitated a cloud transformation. Launched cloud transformation by leading a team of three in an enterprise and vendor application mapping exercise}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Divestiture and Cloud Migration Execution} % Job title
    {} % Organization
    {} % Location
    {Branchburg, New Jersey U.S.A.} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Fourth person onboarded to manage the divestiture of \$8B in assets from a Fortune 50 pharmaceutical company. Set up the operational structure for the application separation factory, oversaw initial application mapping, architected data reporting pathways, built executive reporting dashboards, and PM’d the SWAT team and Architecture Reveiw Board during execution}
        \item {Reconfigured enterprise-wide server uptime requirements during the cloud migration for the pharmaceutical company, resulting in over \$30M saved annually. This effort led to \$75M in follow-on business across spin-co and steer-co, including a ServiceNow implementation, cloud migration, and an IT financial process revamp}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Non-profit and Side Projects} % Job title
    {Other} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {ConstitutionDAO Core Contributor and Founing Member: Contributed as part of a 30-person team that raised \$50M in seven days from 30,000 contributors to bid on a copy of the U.S. Constitution. Served as liaison to Sotheby’s Auction House during the process. Created and pioneered a net new business model for internet native organizations (DAOs) which is still used today. The story of ConstitutionDAO is now a case study in multiple MBA courses}
        \item {OADAO Core Contributor Founding Member: Started an open science nonprofit community of 5000+ people dedicated to the use of emerging technologies to further open science practices in academia. }
        \item {DeSci Ecosystem Steward: Served one year in a non-profit, cross-company role helping nurture an early blockchain based ecosystem. As of November 2024, the DeSci Ecosystem now totals \$1B}
        \item {GOFAIR Fellow: Selected to participate in prestigious data management for AI fellowship for added study on data management best practices in distributed ecosystems}
        \item {BigGreenDAO Launch Consultant: Helped Kimbal Musk and the BigGreen Team ideate on potential operational and business models prior to DAO launch}
      \end{cvitems}
    }

\end{cventries}
